Structuring College Access

### 2025-02-10 index.qmd
test hiding slides from toc
starting presentation in earnest

### Introduction
#### Talent is everywhere, but structure allocates talent to unequal opportunities

@@

POP OUT OF GEOMARKETS

- Chicago
- New York

@@

- Enrollment Planning Service:
- Student Search Service:

**Research questions** focus on metropolitan areas

1. What is SES and racial variation between, within geomarkets? How does this change over time?
1. What is SES and racial composition of included vs. excluded prospects, if student list purchases filter on particular Geomarkets?

### New York and Chicago Geomarkets

@@

## Level-2 heading

### Level-3 heading

### Level-3 heading {.hide}
#### Level-4 subheading

# Empirical Context

@@

### References

>>>>

### Introduction {.hide}
#### Talent is everywhere, but structure allocates talent to unequal opportunities

@@

@@

- Enrollment Planning Service (EPS): software recommends which Geomarkets to recruit and which high schools to visit
- Student Search Service: purchase the contact information of prospects that meet "search filter" criteria

**Research questions** (focus on metropolitan areas):

1. What is SES and racial variation between, within Geomarkets? How does this change over time?
1. What is SES and racial composition of included vs. excluded prospects, if student list purchases filter on particular Geomarkets?

### New York and Chicago Geomarkets {.hide}

@@

# Background

### Background{.hide}
#### Creating Market Segment Model and Geomarkets

Project origins

Market Segment Model

- Allocates students into four market segments based on score-sending behavior of 1980 SAT test-takers
- "local" student submits most SAT scores to institutions in their own Geomarket
- "An “in-state” student submits more SAT scores to in-state institutions than they do to local, regional, or national institutions

Geomarkets

> Zemsky & Oedel (1983) [p. 4] write that,  [Often] the market boundaries match formal political and educational divisions, reflecting natural channels of communication. Each major metropolitan area is composed of several markets, usually corresponding to the inner city, a first ring of suburbs, and an outer ring of suburbs.

@@

### Discussion{.hide}
#### Summary of results

THIS IS TEXT

### Discussion{.hide}
#### Contributin to scholarship

THIS IS TEXT

# References
